%
% How to fix the Underfull \vbox badness has occurred while \output is active on my memoir chapter style?
% https://tex.stackexchange.com/questions/387881/how-to-fix-the-underfull-vbox-badness-has-occurred-while-output-is-active-on-m
%

% ----------------------------------------------------------
\lang
{\chapter[Sample example]{Gertrude Stein - Tender Buttoms - part 3 - Rooms}}
{\chapter[Anexo exemplo]{Como exibir o tamanho da fonte em uso na saída final}}
% ----------------------------------------------------------


% Multiple-language document - babel - selectlanguage vs begin/end{otherlanguage}
% https://tex.stackexchange.com/questions/36526/multiple-language-document-babel-selectlanguage-vs-begin-endotherlanguage
\begin{otherlanguage*}{english}

 

Gertrude Stein
Tender Buttoms - Part 3 - Rooms

Act so that there is no use in a centre. 
A wide action is not a width. A preparation is given to the ones preparing. They do not eat who mention silver and sweet. There was an occupation.
A whole centre and a border make hanging a way of dressing. This which is not why there is a voice is the remains of an offering. There was no rental.
So the tune which is there has a little piece to play, and the exercise is all there is of a fast. The tender and true that makes no width to hew is the time that there is question to adopt.
To begin the placing there is no wagon. There is no change lighter. It was done. And then the spreading, that was not accomplishing that needed standing and yet the time was not so difficult as they were not all in place. They had no change. They were not respected. They were that, they did it so much in the matter and this showed that that settlement was not condensed. It was spread there. Any change was in the ends of the centre. A heap was heavy. There was no change.
The instance of there being more is an instance of more. The shadow is not shining in the way there is a black line. The truth has come. There is a disturbance. Trusting to a baker's boy meant that there would be very much exchanging and anyway what is the use of a covering to a door. There is a use, they are double.
The whole arrangement is established. The end of which is that there is a suggestion, a suggestion that there can be a different whiteness to a wall. This was thought.
A fact is that when the place was replaced all was left that was stored and all was retained that would not satisfy more than another. The question is this, is it possible to suggest more to replace that thing. This question and this perfect denial does make the time change all the time.
The sister was not a mister. Was this a surprise. It was. The conclusion came when there was no arrangement. All the time that there was a question there was a decision. Replacing a casual acquaintance with an ordinary daughter does not make a son.
A little sign of an entrance is the one that made it alike. If it were smaller it was not alike and it was so much smaller that a table was bigger. A table was much bigger, very much bigger. Changing that made nothing bigger, it did not make anything bigger littler, it did not hinder wood from not being used as leather. And this was so charming. Harmony is so essential. Is there pleasure when there is a passage, there is when every room is open. Every room is open when there are not four, there were there and surely there were four, there were two together. There is no resemblance.The time came when there was a birthday. Every day was no excitement and a birthday was added, it was added on Monday, this made the memory clear, this which was a speech showed the chair in the middle where there was copper.
Startling a starving husband is not disagreeable. The reason that nothing is hidden is that there is no suggestion of silence. No song is sad. A lesson is of consequence.
Blind and weak and organised and worried and betrothed and resumed and also asked to a fast and always asked to consider and never startled and not at all bloated, this which is no rarer than frequently is not so astonishing when hair brushing is added. There is quiet, there certainly is.
A silence is not indicated by any motion, less is indicated by a motion, more is not indicated it is enthralled. So sullen and so low, so much resignation, so much refusal and so much place for a lower and an upper, so much and yet more silence, why is not sleeping a feat why is it not and when is there some discharge when. There never is.
The time when there is not the question is only seen when there is a shower. Any little thing is water.
A can containing a curtain is a solid sentimental usage. The trouble in both eyes does not come from the same symmetrical carpet, it comes from there being no more disturbance than in little paper. This does show the teeth, it shows color.
A measure is that which put up so that it shows the length has a steel construction. Tidiness is not delicacy, it does not destroy the whole piece, certainly not it has been measured and nothing has been cut off and even if that has been lost there is a name, no name is signed and left over, not any space is fitted so that moving about is plentiful. Why is there so much resignation in a package, why is there rain, all the same the chance has come, there is no bell to ring.
A package and a filter and even a funnel, all this together makes a scene and supposing the question arises is hair curly, is it dark and dusty, supposing that question arises, is brushing necessary, is it, the whole special suddenness commences then, there is no delusion.
Why is a pale white not paler than blue, why is a connection made by a stove, why is the example which is mentioned not shown to be the same, why is there no adjustment between the place and the separate attention. Why is there a choice in gamboling. Why is there no necessary dull stable, why is there a single piece of any color, why is there that sensible silence. Why is there the resistance in a mixture, why is there no poster, why is there that in the window, why is there no suggester, why is there no window, why is there no oyster closer. Why is there a circular diminisher, why is there a bather, why is there no scraper, why is there a dinner, why is there a bell ringer, why is there a duster, why is there a section of a similar resemblance, why is there that scissor.
South, south which is a wind is not rain, does silence choke speech or does it not.
Giving it away, not giving it away, is there any difference. Giving it away. Not giving it away.
A success, a success is alright when there are there rooms and no vacancies, a success is alright when there is a package, success is alright anyway and any curtain is wholesale. A curtain diminishes and an ample space shows varnish.
Any smile is stern and any coat is a sample. Is there any use in changing more doors than there are committees. This question is so often asked that squares show that they are blotters. It is so very agreeable to hear a voice and to see all the signs of that expression.
Cadences, real cadences, real cadences and a quiet color. Careful and curved, cake and sober, all accounts and mixture, a guess at anything is righteous, should there be a call there would be a voice.
A line in life, a single line and a stairway, a rigid cook, no cook and no equator, all the same there is higher than that another evasion. Did that mean shame, it meant memory. Looking into a place that was hanging and was visible looking into this place and seeing a chair did that mean relief, it did, it certainly did not cause constipation and yet there is a melody that has white for a tune when there is straw color. This shows no face.
Why is there education, there is education because the two tables which are folding are not tied together with a ribbon, string is used and string being used there is a necessity for another one and another one not being used to hearing shows no ordinary use of any evening and yet there is no disgrace in looking, none at all. This came to separate when there was simple selection of an entire preoccupation.
Currents, currents are not in the air and on the floor and in the door and behind it first. Currents do not show it plainer. This which is mastered has so thin a space to build it all that there is plenty of room and yet is it quarreling, it is not and the insistence is marked. A change is in a current and there is no habitable exercise.
A religion, almost a religion, any religion, a quintal in religion, a relying and a surface and a service in indecision and a creature and a question and a syllable in answer and more counting and no quarrel and a single scientific statement and no darkness and no question and an earned administration and a single set of sisters and an outline and no blisters and the section seeing yellow and the centre having spelling and no solitude and no quaintness and yet solid quite so solid and the single surface centred and the question in the placard and the singularity, is there a singularity, and the singularity, why is there a question and the singularity why is the surface outrageous, why is it beautiful why is it not when there is no doubt, why is anything vacant, why is not disturbing a centre no virtue, why is it when it is and why is it when it is and there is no doubt, there is no doubt that the singularity shows.
This is a sound and obligingness more obligingness leads to a harmony in hesitation.
The change is mercenary that settles whitening the coloring and serving dishes where there is metal and making yellow any yellow every color in a shade which is expressed in a tray. This is a monster and awkward quite awkward and the little design which is flowered which is not strange and yet has visible writing, this is not shown all the time but at once, after that it rests where it is and where it is in place. No change is not needed. That does show design.
Sugar any sugar, anger every anger, lover sermon lover, centre no distractor, all order is in a measure.
To consider a lecture, to consider it well is so anxious and so much a charity and really supposing there is grain and if a stubble every stubble is urgent, will there not be a chance of legality. The sound is sickened and the price is purchased and golden what is golden, a clergyman, a single tax, a currency and an inner chamber.
A bridge a very small bridge in a location and thunder, any thunder, this is the capture of reversible sizing and more indeed more can be cautious. This which makes monotony careless makes it likely that there is an exchange in principle and more than that, change in organization.
This cloud does change with the movements of the moon and the narrow the quite narrow suggestion of the building. It does and then when it is settled and no sounds differ then comes the moment when cheerfulness is so assured that there is an occasion.
Dance a clean dream and an extravagant turn up, secure the steady rights and translate more than translate the authority, show the choice and make no more mistakes than yesterday.
This means clearness, it means a regular notion of exercise, it means more than that, it means liking counting, it means more than that, it does not mean exchanging a line.
Why is there more craving than there is in a mountain. This does not seem strange to one, it does not seem strange to an echo and more surely is in there not being a habit. Why is there so much useless suffering. Why is there.
Any wet weather means an open window, what is attaching eating, anything that is violent and cooking and shows weather is the same in the end and why is there more use in something than in all that.
Surprise, the only surprise has no occasion. It is an ingredient and the section the whole section is one season.
A light in the moon the only light is on Sunday. What was the sensible decision. The sensible decision was that notwithstanding many declarations and more music, not even notwithstanding the choice and a torch and a collection, notwithstanding the celebrating hat and a vacation and even more noise than cutting, notwithstanding Europe and Asia and being overbearing, not even notwithstanding an elephant and a strict occasion, not even withstanding more cultivation and some seasoning, not even with drowning and with the ocean being encircling, not even with more likeness and any cloud, not even with terrific sacrifice of pedestrianism and a special resolution, not even more likely to be pleasing. The care with which the rain is wrong and the green is wrong and the white is wrong, the care with which there is a chair and plenty of breathing. The care with which there is incredible justice and likeness, all this makes a magnificent asparagus, and also a fountain.

\end{otherlanguage*}


